Week 3 Notebook

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd

# Week 2: Scripts
## Smuggler's Index: Network Attributes  
  - Edgelist
  - unweghted
  - undirected

Network attributes:

*statnet*
  vertices = 274
  directed = TRUE
  hyper = FALSE
  loops = FALSE
  multiple = FALSE
  bipartite = FALSE
 total edges = 671 
   missing edges = 0 
   non-missing edges = 0 
 density = 0

Edge attributes:
[1]ingTyp:
   character valued attribute

Attribute summary:
  the 10 most common values are:
  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
    135     125     115      84      54      28      19      12       9       7

@@

###   STATNET:   Network Description 
 *statnet*
  vertices = 274
  directed = TRUE
  hyper = FALSE
  loops = FALSE
  multiple = FALSE
  bipartite = FALSE
 total edges = 671 
   missing edges = 0 
   non-missing edges = 0 
 density = 0

Edge attributes:

 ingTyp:
   character valued attribute
   attribute summary:
   the 10 most common values are:
  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
    135     125     115      84      54      28      19      12       9       7 
```{r statnet: Network Summary & Attribute info, echo=TRUE}

@@

component.dist(
  snEL, 
  connected= c("unilateral")) # c("strong","weak","unilateral","recursive"))

component.largest(
  snEL, 
  connected = c("unilateral"), #=c("strong","weak","unilateral" "recursive")
  result = c("graph"), #c("membership", "graph") 
  return.as.edgelist = FALSE)

@@

@@

@@

summary(geodist(snEL, 
        inf.replace=Inf, 
        count.paths=TRUE, # include geodesics 
        predecessors=FALSE,# include predecessor list
        ignore.eval=FALSE, # ignore edge values
        na.omit=FALSE) # remove NA-values edges
        )
```

@@

# Head
head(V(igEL)$name,10)
head(E(igEL)$ingTyp, 10)

#Tail
tail(V(igEL)$name,10)
tail(E(igEL)$ingTyp, 10)

@@

  # 20 Vertex Names

      Head, 10 + Tail, 10
 [1] "AKU AKU"                    
 [2] "(1-INCH-SQUARE) CHUNKS PINEAPPLE"    
 [3] "MINT LEAVES"                
 [4] "LIME JUICE"    
 [5] "DEMERARA SYRUP"             
 [6] "PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)"
 [7] "BLENDED LIGHTLY AGED RUM"   
 [8] "PUPULE" 
 [9] "ORANGE JUICE"               
 [10] "CINNAMON SYRUP"
 [1] "SINGAPORE SLING"                     
      "BENEDICTINE"
      "HONDO HATTIE'S JUNGLE PUNCH!"    
  [4] "KAHIKO PUNCH"
      "PASSION FRUIT HONEY"                 
      "TRIUMVIRATE PUNCH"   
  [7] "EUREKA PUNCH"                         
      "YULETIDAL WAVE"
      "RUMBUSTION PUNCH"                
 [10] "PUKA PUNCH"

@@

@@

all_shortest_paths(igEL,
                     "AKU AKU" ,
                     "SINGAPORE SLING",
                     weights=NA)$res

all_shortest_paths(igEL,
                   "AKU AKU",
                   "HONDO HATTIE'S JUNGLE PUNCH!",
                   weights=NA)$res

all_shortest_paths(igEL,
                   "AKU AKU",
                   "KAHIKO PUNCH",
                   weights=NA)$res

all_shortest_paths(igEL,
                     "AKU AKU", 
                     "PASSION FRUIT HONEY",
                     weights=NA)$res

all_shortest_paths(igEL,
                   "AKU AKU",
                   "TRIUMVIRATE PUNCH",
                   weights=NA)$res

  all_shortest_paths(igEL,"AKU AKU",
                     "EUREKA PUNCH",
                     weights=NA)$res

  all_shortest_paths(igEL,"AKU AKU", 
                     "YULETIDAL WAVE" ,
                     weights=NA)$res

  all_shortest_paths(igEL,
                     "AKU AKU" ,
                     "RUMBUSTION PUNCH",
                     weights=NA)$res

  all_shortest_paths(igEL,
                     "AKU AKU" ,
                     "PUKA PUNCH",
                     weights=NA)$res
```

6.  *triads or transitivity,*

@@

```{r statnet: Dyad Census , echo=TRUE}
library(statnet)
    sna::dyad.census(snEL)

```
```{r iGraph: Dyad Census, echo=TRUE}
library(igraph)

@@

@@

#     total number of all four triad types returned by triad census
   sum(
     sna::triad.census(
       snEL,
       mode="graph")
     )

@@

   sna::triad.classify(
     snEL,
     tri=c(1,2,3),
     mode==c("digraph")
   )
  #Classify the triads (1,2,3) and (2,3,4)

   triad.classify(snEL,tri=c(1:14))
   gplot(snEL,c[1:14])

@@

```{r iGraph: Triad Census, echo=TRUE}
library(igraph)
#Classify all Triad in the network
     igraph::triad_census(igEL)

@@

#     network transitivity:
    transitivity(igEL)

#     weighted network transitivity:
#   igraph::transivity(igEL)

@@

## Local Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

```{r iGraph:Local transitivity, echo=TRUE}

#     Retrive a list of the vertices we are interested
    V(igEL)[c("" ,
                "", 
                "Medici",
                "")]

#     check ego network transitivity
transitivity(igEL,
             type="local", 
             vids=V(igEL)
             [c("",
                "", 
                "Medici",
                "")]) 
#     get global clustering cofficient
  transitivity(igEL, type="global")

@@

@@

7.  *connectedness and.or component structure, etc.*

> Distill is a publication format for scientific and technical writing, native to the web.
>
> Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.
##

>>>>

# Week 2: Scripts
## Smuggler's Index: Network Attributes

@@

###   STATNET:   Network Description

```{r statnet: Network Summary & Attribute info, echo=TRUE}

@@

cd_snEL<- component.dist(
  snEL, 
  connected= c("strong")) # c("strong","weak","unilateral","recursive"))
  summary(cd_snEL)    
  View(cd_snEL)

  gplot.layout.circle(cd_snEL)

cl_snEL <- component.largest(
  snEL, 
  connected = c("strong"), #=c("strong","weak","unilateral" "recursive")
  result = c("graph"), #c("membership", "graph") 
  return.as.edgelist = FALSE)

  view(summary(cl_snEL))
  View(cl_snEL)

gplot(cl_snEL)

@@

```{r STATNET: Plot: Geodesic: Numbers and Lengths }
library(statnet)
library(sna)

  gd_snEL <- geodist(
    snEL, 
    inf.replace=Inf, 
    count.paths=TRUE, 
    predecessors=FALSE,
    ignore.eval=TRUE, 
    na.omit=TRUE)

   summary(gd_snEL)
  gplot(gd_snEL)

  #Examine the number of geodesics
snEL_gdCounts <- gd_snEL$counts

#Examine the geodesic distances
snEL_gdist  <- gd_snEL$gdist

@@

  reachability(
    snEL,
    geodist.precomp=NULL,
    return.as.edgelist=FALSE,
    na.omit=FALSE)

@@

summary(geodist(snEL, 
        inf.replace=Inf, 
        count.paths=TRUE, # include geodesics 
        predecessors=FALSE,# include predecessor list
        ignore.eval=FALSE, # ignore edge values
        na.omit=FALSE) # remove NA-values edges
        )

#Examine the number of geodesics
gd_snEL$counts

#Examine the geodesic distances
gd_snEL$gdist

  summary(gd_snEL)
  gplot(gd_snEL)

@@

@@

@@

```{r iGraph:Nodes: Path: Length, echo=TRUE}
library(igraph)
# Head
list(
  head(V(igEL)$name,10),
  tail(V(igEL)$name,10)
  )

@@

aku_Sing <- all_shortest_paths(igEL,
                     "AKU AKU" ,
                     "SINGAPORE SLING",
                     weights=NA)$res

aku_Hondo <- all_shortest_paths(igEL,
                   "AKU AKU",
                   "HONDO HATTIE'S JUNGLE PUNCH!",
                   weights=NA)$res

aku_Kahiko <- all_shortest_paths(igEL,
                   "AKU AKU",
                   "KAHIKO PUNCH",
                   weights=NA)

aku_PFhoney <- all_shortest_paths(igEL,
                     "AKU AKU", 
                     "PASSION FRUIT HONEY",
                     weights=NA)$res

aku_Trium <- all_shortest_paths(igEL,
                   "AKU AKU",
                   "TRIUMVIRATE PUNCH",
                   weights=NA)$res

aku_Eureka <- all_shortest_paths(igEL,"AKU AKU",
                     "EUREKA PUNCH",
                     weights=NA)$res

aku_YuleTide <- all_shortest_paths(igEL,"AKU AKU", 
                     "YULETIDAL WAVE" ,
                     weights=NA)$res

aku_Rumbustion <-   all_shortest_paths(igEL,
                     "AKU AKU" ,
                     "RUMBUSTION PUNCH",
                     weights=NA)$res

aku_Puka <-   all_shortest_paths(igEL,
                     "AKU AKU" ,
                     "PUKA PUNCH",
                     weights=NA)$res
```

@@

```{r iGraph: Dyad Census, echo=TRUE}
library(igraph)

@@

```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}

graph.density(igEL)
    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network

      # Generating a random graph for comparison
# ?erdos.renyi.game
      ## In an erdos.renyi.graph, each edge has the same probability of being created. We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.

igELNod <- vcount(igEL)

igELDen <- graph.density(igEL)

smugEL_DigRandoG <- 
  erdos.renyi.game(
    n = igELNod, 
    p.or.m = igELDen, 
    directed = T) 
      # where n is the number of nodes, 
      # p.or.m is the probability of drawing an edge, 
      #directed is whether the network is directed or not

#**plot(smugEL_DigRandoG, ...** in .R notebook  
     # vertex.size = 5, 
     # vertex.label = 1, 
     # edge.curved = .1, 
     # vertex.color = "tomato", 
     # edge.arrow.size = .1, 
     # edge.width = .5, 
     # edge.color = "grey60")

```{r statnet: Dyad Census , echo=TRUE}
library(statnet)

  sna::dyad.census(snEL)

  network.dyadcount(snEL)

```{r statnet: grecip: dyadic reciprocity & Mutuality, echo=TRUE}
library(statnet)
library(sna)

#  the number of complete dyads (i.e., i<->j)
mutuality(snEL)

  grecip(snEL)

    #proportion of symmetric dyads
  grecip(snEL, 
         measure = "dyadic")

      # returns the ratio of mutuals to non-null dyads.
  grecip(snEL, 
         measure = "dyadic.nonnull")

      # the proportion of edges which are reciprocated
  grecip(snEL, 
         measure = "edgewise")

      # returns the log of the ratio of the edgewise reciprocity to the density
  grecip(snEL, 
         measure = "edgewise.lrr")

  # The correlation measure may be interpreted as the net tendency for edges of similar relative value (with respect to the mean edge value) to occur within the same dyads.

  grecip(snEL, 
         measure = "correlation")

@@

#     total number of all four triad types returned by triad census
snEL_sumTCensus  <- sum(
  sna::triad.census(
    snEL,
    mode="graph"))

@@

list(   sna::triad.classify(
     snEL,
     tri=c(1,2,3),
     mode==c("digraph")
   ))
  #Classify the triads (1,2,3) and (2,3,4)

   triad.classify(snEL,tri=c(1:5))
   gplot(snEL,c[1:5])

@@

```{r iGraph: Triad Census, echo=TRUE}
library(igraph)
#Classify all Triad in the network
list(igraph::triad_census(igEL))

@@

#     network transitivity:
summary(
  transitivity(igEL)
)

summary(
igEL_guTrans <- transitivity(igEL,
             type = c("globalundirected"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
             isolates = c("NaN", "zero"))
)

summary(
  transitivity(igEL,
             type = c(
               "average"),
             vids = NULL, #  all vertices are considered.
             weights = NULL,
             isolates = c("NaN", "zero"))
)

#   c("undirected", "global", "globalundirected", "localundirected", "local","average", "localaverage","localaverageundirected", "barrat", "weighted")

@@

## Ego Network Transivity or Clustering
`Local transitivity` (local clustering coefficient), is a technical description of the density of an ego network.

, "KAHIKO PUNCH", "TRIUMVIRATE PUNCH", "EUREKA PUNCH", 
                "YULETIDAL WAVE",
                "RUMBUSTION PUNCH",
                "PUKA PUNCH"
```{r iGraph:Local transitivity, echo=TRUE}
#     get global clustering cofficient
  transitivity(igEL, type="global")

@@

#     check ego network transitivity
transitivity(igEL,
             type="local", 
             vids=V(igEL)[c(
               "AKU AKU", "SINGAPORE SLING", "HONDO HATTIE'S JUNGLE PUNCH!")]
               )
```

## Component Structure and Membership

### Statnet: Component STructure, Isolates, Density
```{r Statnet: Isolates, echo=TRUE}

              ## Isolates:

 #List the isolates
 isolates(snEL)

 # Returns a list of the isolates in the graph or graph set
 isolates(snEL, diag=FALSE)

 # Is Ego an Isolate?
 is.isolate(snEL, ego_exp, g=1, diag=FALSE)

 # Adds n isolates to the graph (or graphs)
 add.isolates(snEL, n_umber, return.as.edgelist = FALSE)

@@

```{r Statnet: Network Density, echo=TRUE}

            # get network density: with possible loops
   network.density(snEL)
          ##**WARNING: Network is multiplex - no general way to define density.**

 # get network density **with** loops: statnet
 gden(snEL, diag=F)

### Igraph: Component STructure, Isolates,
```{r iGraph: Undirected: Component Structure, echo=TRUE}
                ## Component Structure:

    # Number of components
 igraph::components(igEL)$no 
      ##**NOTE:** $no prevents a list of components from being printed

# Size of each component
 igraph::components(igEL)$csize

```{r iGraph: Undirected: network density, echo=TRUE}

    #get network density **with** loops
 network.density(igEL)
 class(igEL)
          ##**NOTE** provides an incorrect density calculation 
          ## as the default assumes that loops are not included but does not remove them

```
 **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.

 Therefore, the default calculation includes the loops in the numerator but not the denominator of the density calculation.

# Week 3:

## Network Density

 The density of a network is defined as the proportion of ties present out of all possible ties in a network.

 **Note:**

 the network density command ignores edge values at present.

 If loops are present or there are multiple edges between two nodes, then the results may not make sense.

```{r Statnet: Network Density, echo=TRUE}

            # get network density: with possible loops
   network.density(snEL)
          ##**WARNING: Network is multiplex - no general way to define density.**

 # get network density **with** loops: statnet

  gden(snEL, diag=F)

 **Igraph** provides an incorrect density calculation as the default assumes  that loops are not included but does not remove them.

```{r iGraph: edge density, echo=TRUE}
library(igraph)
    #get network density **with** loops
edge_density(igEL, loops = FALSE)

 class(igEL)
          ##**NOTE** provides an incorrect density calculation 
          ## as the default assumes that loops are not included but does not remove them

## Vertex Degree
 **Vertex degree** is a description of an individual node; each vertex in a network may have a different node degree.

 *Node Degree:*
   node degree is one measure of node centrality or popularity; 
 Node degree cis a count of the relationships that a node is involved in or the count of the edges that are incident to a vertex

 **use the network degree command to:**
   *  compute network summary statistics (such as average network degree);
 *  graph the network degree distribution; or
 *  identify particular nodes (such as the five nodes with the most contacts).

```{r Statnet: Vertex Degree, echo=TRUE}
library(statnet)
library(sna)
      # statnet: Calculate average network degree
summary(sna::degree(snEL, 
             g=1, 
             nodes=NULL, 
             gmode="digraph", #directed;
             diag=FALSE, #excludes diagonals 
             tmaxdev=FALSE, 
             cmode="indegree", 
             rescale=FALSE, 
             ignore.eval=FALSE))
          # ignores loops or self-nominations 
summary(
  snEL_vd <- sna::degree(snEL, 
             g=1, 
             nodes= NULL, 
             gmode="graph", #undirected
             diag=TRUE, #includes diagonals 
             tmaxdev=F, 
             cmode="freeman", 
             rescale=F, #  scores rescaled to sum to 1.
             ignore.eval=FALSE))
plot(snEL_vd)
#**cmode=* degree centrality being computed. 
#*"indegree"
#*"outdegree"
#**DEFAULT*"freeman" refer to the indegree, outdegree, 
#*total (Freeman) degree measures, respectively. 
```

```{r iGraph: Undirected: Vertex Degree, echo=TRUE}
# igraph: Calculate average network degree
 # provides node name along with node degree

 # includes loops
  plot(igraph::degree(igEL))

## Network Degree Summary Statistics

```{r Statnet: , echo=TRUE}
library(statnet)
library(sna)   
   # Basic R: get summary statistics for node attributes

summary(snEL_Deg <- 
           sna::degree(snEL))
    plot(snEL_Deg)

      # provides range, mean, median and standard deviation of a vector.

 # get summary statistics for node degree for the binary network degree

snEL_degVtx <- data.frame(
   name=snEL%v%"vertex.names",
   totdegree=sna::degree(snEL),
   indegree=sna::degree(snEL, cmode="indegree"),
   outdegree=sna::degree(snEL, cmode="outdegree"))
gplot(snEL_degDF)

snEL_degVtx <- data.frame(
   name=snEL%v%"vertex.names",
   totdegree=sna::degree(snEL))

   gplot(snEL_degDF)
  summary(snEL_degVNme)

snEL_degVNme <- data.frame(
   name=snEL%v%"Aku Aku",
    outdegree=sna::degree(snEL, cmode="outdegree"))
   gplot(snEL_degVNme)
    summary(snEL_degVNme)

snEL_degVNme <- data.frame(
   name=snEL%v%"(1-INCH-SQUARE) CHUNKS PINEAPPLE",
   indegree=sna::degree(snEL, cmode="indegree"))

gplot(snEL_degVNme)
summary(snEL_degVNme)

snEL_degVNme <- data.frame(
   name=snEL%v%"MINT LEAVES",
   outdegree=sna::degree(snEL, cmode="outdegree"))

gplot(snEL_degVNme)
summary(snEL_degVNme)

snEL_degVNme <- data.frame(
   name=snEL%v%"DEMERARA SYRUP",
   outdegree=sna::degree(snEL, cmode="outdegree"))

gplot(snEL_degVNme)
summary(snEL_degVNme)

odeg_peachLqr <- data.frame(
   name=snEL%v%"PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)",
   outdegree=sna::degree(snEL, cmode="outdegree"))
gplot(odeg_peachLqr)
summary(odeg_peachLqr)

odeg_blaRum <- data.frame(
   name=snEL%v%" BLENDED LIGHTLY AGED RUM",
   outdegree=sna::degree(snEL, cmode="outdegree"))
gplot(out_blaRum)
summary(out_blaRum)

odeg_val3 <- data.frame(

   outdegree=sna::degree(snEL, cmode="outdegree"))

 6/274 vertices, named, from 1bfe0b4:
[1] (1-INCH-SQUARE) CHUNKS PINEAPPLE                     
[2] MINT LEAVES                                          
[3] LIME JUICE                                           
[4] DEMERARA SYRUP                                       
[5] PEACH LIQUEUR (SUCH AS MATHILDE, COMBIER, OR GIFFARD)
[6] BLENDED LIGHTLY AGED RUM

## Centrilization

```{r iGraph: Undirected: DEGREE CENTRALITY: dnkIng}
library(igraph)
library(tidyverse)

plot(centr_degree(igEL)$res)

summary(
  centr_degree(igEL,
  mode = c("all"),
  loops = TRUE,
  normalized = TRUE)$res)

plot(
  centr_degree(igEL,mode = c("all"))$res)

summary(
centr_degree(igEL,
  mode = c("all"),
  loops = TRUE,
  normalized = TRUE)$centralization
)

summary(
centr_degree(igEL,
  mode = c("all"),
  loops = TRUE,
  normalized = TRUE)$theoretical_max
)

## Degree Centrality
We can break large social networks down into their constituent parts. These constituent parts are referred to as “motifs”. The most basic motif consists of two nodes and is called a dyad. Edges in a network signify the presence or absence of dyadic relations. It follows that a dyad in an undirected network can have two unique configurations: connected or disconnected; and three unique configurations in a directed network (mutual, assymetric, and null

```{r iGraph: Directed: GRAPH: Dyad Census, echo=TRUE}

graph.density(igEL)
    ## Density captures, at the macro-level, the proportion of dyads that are present over the possible total number of dyads in the network

      # Generating a random graph for comparison
# ?erdos.renyi.game
      ## In an erdos.renyi.graph, each edge has the same probability of being created. We determine the probability and it returns a random graph with a density that equals (in expectation) this probability.

igELNod <- vcount(igEL)

igELDen <- graph.density(igEL)

smugEL_DigRandoG <- 
  erdos.renyi.game(
    n = igELNod, 
    p.or.m = igELDen, 
    directed = T) 
      # where n is the number of nodes, 
      # p.or.m is the probability of drawing an edge, 
      #directed is whether the network is directed or not

#**plot(smugEL_DigRandoG, ...** in .R notebook  
     # vertex.size = 5, 
     # vertex.label = 1, 
     # edge.curved = .1, 
     # vertex.color = "tomato", 
     # edge.arrow.size = .1, 
     # edge.width = .5, 
     # edge.color = "grey60")

```{r iGraph: Directed: Degree Centrality}
# Degree centrality is calculated using the degree function in R. It returns how many edges each node has.
view(degree(igEL))

ingT_deg <- igEL
V(ingT_deg)$degree <- degree(ingT_deg) # assignment

# plot(ingT_deg, 
#     vertex.label.cex = .6, 
#     vertex.label.color = "black", 
#     vertex.size = V(igEL)$degree, 
#     vertex.label.cex = .2) # sized by degree

```{r iGraph: Directed: Betweenness Centrality}

view(betweenness(igEL, directed = FALSE))

# view(betweenness(igEL, directed = TRUE))
              # Yeilds 0

ingTypEL_Between <- igEL
# We can again assign the output of betweenness() to a variable in the network and size the nodes according to it.

V(ingTypEL_Between)$betweenness <- 
  betweenness(ingTypEL_Between, 
              directed = F)

# plot(ingTypEL_Between, 
#     vertex.label.cex = .6, 
#     vertex.label.color = "black", 
#     vertex.size = V(ingTypEL_Between)$betweenness) # sized by betweenness

```{r iGraph: UnDirected:  Closeness Centrality}

view(closeness(igEL))

  # We assign it to a node variable and plot the network, adjusting node size by closeness.
ingTyp_Cent <- igEL #**UNDIRECTED **

V(ingTyp_Cent)$closeness <- closeness(ingTyp_Cent)

View(ingTyp_Cent)

# plot(ingTyp_Cent,
#     vertex.label.cex = .6, 
#     vertex.label.color = "black", 
#     vertex.size = V(ingTyp_Cent)$closeness/max(V(ingTyp_Cent)$closeness) * 20)

Degree centrality only takes into account the number of edges for each node, but it leaves out information about ego’s alters
```{r iGraph: Directed: Eigenvector Centrality}

view(evcent(igEL)$vector)
# view(evcent(igEL)$vector)
ingTyp_Vector <- igEL
V(ingTyp_Vector)$eigenvector <- evcent(ingTyp_Vector)$vector

# plot(ingTyp_Vector,
#     vertex.label.cex = .6, 
#     vertex.label.color = "black", 
#     vertex.size = V(ingTyp_Vector)$eigenvector/max(V(ingTyp_Vector)$eigenvector) * 20)
```

```{r iGraph: Directed: Bonacich Centrality}

ingTyp_Cent <- igEL

V(ingTyp_Cent)$bonacich <- 
  power_centrality(ingTyp_Cent, exponent = -2, rescale = T)

V(ingTyp_Cent)$bonacich <- 
  ifelse(V(ingTyp_Cent)$bonacich < 0, 0, V(ingTyp_Cent)$bonacich)
```

```{r iGraph: Directed: Page Rank}

ingTyp_Cent <- igEL

V(ingTyp_Cent)$page_rank <- page_rank(ingTyp_Cent, directed = TRUE)$vector

 plot(ingTyp_Cent,
     vertex.label.cex = .6, 
     vertex.label.color = "black", 
     vertex.size = V(ingTyp_Cent)$page_rank/max(V(ingTyp_Cent)$page_rank) * 20)

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/week3_Plots/Scripts_week3_Plots.Rmd

>>>>

#: Visualization: ggplot2
```{r Visualization: ggplot2}

# Dependencies
 library(network)
 library(sna)
 library(ggplot2)

library(visNetwork)
library(threejs)
 library(networkD3)
 library(ndtv)
 # ggnetwork - This package allows to pass network objects to ggplot2 and provides geometries to plot their elements.

 library(ggnetwork)

  # visualize your network graphs 
 library(GGally)

## [network visualization with ggplot2]

# graph the SMUG network

smug_attributes <- smugCovIdx
smug_edj <- smugCovIdx[2:3]
View(smug_edj)
#V1: dnkIng
#V2: ingTyp

smugNet <- 
  graph.edgelist(as.matrix(smug_edj), directed = T)

V(smugNet)$dnkIng <- 
  smug_attributes$dnkIng[match(V(smugNet)$name, smug_attributes$ingTyp)]

V(smugNet)$dnkNam <- 
  smug_attributes$dnkNam[
    match(V(
      smugNet)$name,
      smug_attributes$dnkIng)
    ]
summary(smugNet)

###**PLOT** in .R Doc
